Incremental Construction of Programs in a Multitask Setting

### 2013-10-23 drafts/nips/nips2013.tex
merged

Performing the minimization operation in equation (\ref{eq:gmax}) is generally difficult.
We approximate the description length of the grammar by the number of unique program fragments in the grammar, multiplied by a regularization constant.
The description length of a program is approximated by the number of (not necessarily unique) program fragments in its smallest parse tree given the grammar.
A slight generalization of the Neville-Manning algorithm then permits tractible approximate maximization of (\ref{eq:gmax}).
Estimation of the production probabilities of $G$ is performed as in \cite{ijcai}.

@@

Learning the structure of graphical models that capture the independencies underlying a dataset is an active area of research\cite{adams-wallach-ghahramani-2010a}\cite{ISI:000240797500002}\cite{ISI:000178037200004}\cite{ISI:A1995RX35400001}. Graphical model structures enforce the conditional independences a modeler believes exists among latent and observed random variables\cite{DBLP:books/daglib/0066829}.
In practice, the sorts of graphical models that humans design, such as Hidden Markov Models, phylogenetic trees, topic models, and Ising models, exhibit certain symmetries and recursive structures that might be amenable to synthesis by programs.

\begin{figure}[h]
% \centering
\begin{minipage}[t]{.4\textwidth}
% \vspace{0pt}
% \begin{subfigure}{.45\textwidth}
  % \vspace*{\fill}
  % \centering
  \includegraphics[width=\linewidth]{./figures/tasks.pdf}
  \caption{Example input/output pairs of learned programs. Each induced program takes as input a list of observed nodes and produces an undirected graphical model. Here, we show each program with a small number of input nodes, but the learned programs transfer arbitrary length lists of visible nodes into the corresponding graphs. Labeled nodes correspond to observed variables; unlabeled nodes correspond to latent variables.}
  \label{fig:tasks}
\end{minipage}
\hspace{1cm}
\begin{minipage}[t]{.5\textwidth}
% \vspace{\fill}
  \includegraphics[width=\linewidth]{./figures/GraphCombinators.pdf}
  \caption{The operation of the undirected unions. Union: computes union of vertexes and edges. UnionC: adds edges between corresponding vertexes. UnionHT: adds edge between first (head) vertex and last (tail) vertex. UnionD: relabels input graph vertices so that they do not overlap and then computes union.}
  \label{fig:graphcomb}\par\vfill
% \end{subfigure}
\end{minipage}
\end{figure}

@@

\subsection{Relation to Prior Work}

MH sampling of programs, ILP, Kitzelman, graph grammars

\subsection{Limitations of SEC}

Does not look at data. Does everything top-down. Blind to the utility of trying one program versus another (no active learning)

\bibliographystyle{plain}
\bibliography{eyal_bib}

>>>>

Performing the minimization operation in equation (\ref{eq:gmax}) is generally difficult.
We approximate the description length of the grammar by the number of unique program fragments in the grammar, multiplied by a regularization constant.
The description length of a program is approximated by the number of (not necessarily unique) program fragments in its smallest parse tree given the grammar.
A slight generalization of the Neville-Manning algorithm then permits tractible approximate minimization of (\ref{eq:gmax}).
Estimation of the production probabilities of $G$ is performed as in \cite{DBLP:conf/ijcai/DechterMAT13}.

@@

Learning the structure of graphical models that capture the independencies underlying a dataset is an active area of research\cite{adams-wallach-ghahramani-2010a}\cite{ISI:000240797500002}\cite{ISI:000178037200004}\cite{DBLP:journals/corr/abs-1302-6815}. Graphical model structures enforce the conditional independences a modeler believes exists among latent and observed random variables\cite{DBLP:books/daglib/0066829}.
In practice, the sorts of graphical models that humans design, such as Hidden Markov Models, phylogenetic trees, topic models, and Ising models, exhibit certain symmetries and recursive structures that might be amenable to synthesis by programs.

\begin{figure}[h]
% \centering
\begin{minipage}[t]{.4\textwidth}

  \includegraphics[width=\linewidth]{./figures/tasks.pdf}
  \caption{Example input/output pairs of learned programs. Each induced program takes as input a list of observed nodes and produces an undirected graphical model. Here, we show each program with a small number of input nodes, but the learned programs transfer arbitrary length lists of visible nodes into the corresponding graphs. Labeled nodes correspond to observed variables; unlabeled nodes correspond to latent variables.}
  \label{fig:tasks}
\end{minipage}
\hspace{0.2in}
\begin{minipage}[t]{.5\textwidth}
  \includegraphics[width=\linewidth]{./figures/GraphCombinators.pdf}
  \caption{The operation of the undirected unions. Union: computes union of vertexes and edges. UnionC: adds edges between corresponding vertexes. UnionHT: adds edge between first (head) vertex and last (tail) vertex. UnionD: relabels input graph vertices so that they do not overlap and then computes union.}
  \label{fig:graphcomb}\par\vfill
% \end{subfigure}
\end{minipage}
\end{figure}

@@

To be clear, what we have shown so far does not provide a way to learn the structure of a graphical model directly from observed data. Rather, this work suggests that we may be able to learn automatically an inductive bias that will subsequently make learning graphical model structures more efficient. Some of the programs that SEC includes in its library correspond to graph transformations, and we think that using this transformations as search operators will make structure learning of graphical models with latent variables a more tractable proposition than it currently is.

The notion that an appropriate inductive bias might help in the structure learning of graphical models is not new: \citep{DBLP:conf/icml/HonorioS10} shows that the inductive bias induced via multitask learning helps a search algorithm find accurate graphical model structures. But while work in this field has focused on how to evaluate a given graph, we hope to show that SEC can learn appropriate search operators directly from a set of training examples.

We have presented the SEC algorithm in the context of learning graph structures, but we note that SEC is a general purpose multitask program induction algorithm. For an excellent survey of the current state of inductive programming systems, see~\citep{DBLP:conf/aaip/Kitzelmann09}.

\bibliographystyle{plainnat}
\bibliography{main}
